Peer influences in air travel behavior: A social autoregressive analysis

### 2015-04-24 article/article.Rmd
Forced adjacency matrices to be symmetric.

# export graph edges as adjacency matrix
matrix_list <- list()
for(i in names(friend_connections)[-(1:2)]){
  matrix_list[[i]] <- get.adjacency(user_graph, type = "both", i)

  # TODO force symmetric
}
```

>>>>

# export graph edges as adjacency matrix
matrix_list <- list()
for(i in names(friend_connections)[-(1:2)]){
  mat <- as.matrix(get.adjacency(user_graph, type = "both", i))
  # force matrix to be symmetric
  matrix_list[[i]] <- pmax(mat, t(mat))
}
```
